\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage[dvipsnames]{xcolor}
\usepackage{float}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheadTwo}[2]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubhead}[3]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\normalsize#3}
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\link}[2]{{\color{blue}\href{#1}{#2}}}

% \newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%              CV STARTS HERE              %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING-----------------
\begin{center}
\textbf{\huge Phuong-Linh Huynh-Ha}
\end{center}
\begin{center}
% \begin{tabular*}{\textwidth}{r@{\extracolsep{\fill}}l}
\begin{tabular*}{0.8\textwidth}{r@{\extracolsep{\fill}}l}
% \begin{tabular*}{\textwidth}{r|l}
Ho Chi Minh City, Vietnam, (+84) 818-697-888 & Email \href{mailto:huynhhaphuonglinh@gmail.com}{huynhhaphuonglinh@gmail.com}\\
LinkedIn \href{https://www.linkedin.com/in/hhplinh}{https://www.linkedin.com/in/hhplinh} &  Github \href{https://github.com/hhplinh}{https://github.com/hhplinh}
\end{tabular*}
\end{center}


% %----------SUMMARY-----------------
% \section{Summary}
%   \resumeSubHeadingListStart
%     \resumeItemListStart
%       \resumeItem{Software Engineer Intern at Google in 2019, Facebook in 2017 \& 2018}
%       \resumeItem{IOI 2015 gold medalist, ICPC World Finals 2016, 2017 \& 2019}
%       \resumeItem{Experience with C++, Java, JavaScript, PHP, OCaml, HTML, Hack \& React}
%     \resumeItemListEnd
%   \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Research Experience}
  \resumeSubHeadingListStart

    \resumeSubhead
      {KIT Computer Vision Lab -- Kyoto Institute of Technology (KIT)}{Jan. 2026 -- Mar. 2026}
      {Incoming Research Intern -- Global Internship Program}
      \resumeItemListStart
      	\resumeItem{Selected for a competitive KIT internship program for partner university students.}
      	\resumeItem{Will conduct research on 3D shape and motion estimation from multi-view images, focusing on 3D reconstruction and dynamic scene understanding.}
      \resumeItemListEnd

      
    \resumeSubhead
      {Software Engineering Laboratory– SELab HCMUS}{Aug. 2025 -- Present}
      {Thesis - Supervised by Assoc. Prof Minh-Triet Tran on Computer Vision}
      \resumeItemListStart
      	\resumeItem{Researching on 3D shape and motion analysis, 3D reconstruction and dynamic scene understanding.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------Publications-----------------
\section{Selected Publications}
    \resumeSubHeadingListStart
        \resumeItem{Hoang-Phuc Nguyen, \underline{\textbf{Phuong-Linh Huynh-Ha}},  Minh-Triet Tran. \textcolor{BlueViolet}{\textbf{Generalizability Evaluation and Anchor-Guided Approach for Category-Agnostic Pose Estimation}}. SOICT 2025, Springer CCIS.}

    \resumeSubHeadingListEnd

%-----------EDUCATION------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubhead
        {University of Science, VNU-HCM (HCMUS), Ho Chi Minh City, Vietnam}{Sep. 2022 -- Present}
        {Advanced Program in Computer Science;  GPA: 3.9/4.0}
        \resumeItemListStart
            \resumeItem{Merit-Based Scholarship \textbf{(Top 4 GPA)} in Semester 2, 2024-2025.}
            \resumeItem{Achieved Top 1.9\% score on the VNU-HCMC Assessment Test (HSA)}
            \resumeItem{Review coursework: Artificial Intelligence, Computer Vision, Computer Systems, General Physics I, II, III, Information Retrieval, Natural Language Processing, Linear Algebra, Statistics, Data Structures, Discrete Structures, Logical Structures, Calculus,  Database, Scientific Method, Technical Writing, OOP, Computer Hardware, Mobile Application Development, Group Theory, Software Engineering. }
        \resumeItemListEnd
    \resumeSubhead
        {Le Khiet High School for the Gifted, Quang Ngai, Vietnam}{Sep. 2019 -- Jun. 2022}
        {Major in English; GPA: 9.7/10.0}
        \resumeItemListStart
            \resumeItem{\textbf{Bronze Medal} in the National Olympiad in English, held by Vietnam Ministry of Education and Training.}
            \resumeItem{\textbf{Consistently ranked Top 1 GPA} throughout all years of the gifted English student program.}
        \resumeItemListEnd
  \resumeSubHeadingListEnd
    
%-----------AWARDS----------
\section{Selected Achievements and Awards}
  \resumeSubHeadingListStart

    \resumeSubheadTwo
      {Artificial Intelligence Olympiad for University students - Preliminary Round}{Nov. 2025}
      \resumeItemListStart
        \resumeItem{Competed in a team of 3, \textbf{Champion} across all Region Preliminary Rounds of the Artificial Intelligence Olympiad for University students.}
      \resumeItemListEnd

    \resumeSubheadTwo
      {Merit-Based Scholarship (Top 4 Ranking), APCS Program}{Semester 2, 2024-2025}
      \resumeItemListStart
        \resumeItem{Awarded the Merit-Based Scholarship for students in the Advanced Program in Computer Science (APCS) by the Faculty of Information Technology, ranking in the \textbf{Top 4} of the entire K22 cohort.}
      \resumeItemListEnd    

    \resumeSubheadTwo
      {Boschler IT 2024}{Sep. 2024}
      \resumeItemListStart
        \resumeItem{Achieved \textbf{Best Team (First Place)} by utilizing the Agile Scrum Framework to design and execute a complex e-commerce solution, applying the Strategy and Chain of Responsibility Design Patterns for flexible vendor management and efficient order fulfillment.}
      \resumeItemListEnd
      
    \resumeSubheadTwo
      {HCMUS-CTF 2024}{Dec. 2024}
      \resumeItemListStart
        \resumeItem{Top \textbf{6 Finalist} in the Capture-The-Flag competition hosted by Ho Chi Minh City University of Science.}
      \resumeItemListEnd

    \resumeSubheadTwo
      {Vietnam National Olympiad in English}{Apr. 2022, Feb. 2021}
      \resumeItemListStart
        \resumeItem{\textbf{Bronze Medal} in 2022 and \textbf{Honorable Mention} in 2021, awarded by the Vietnam Ministry of Education and Training.}
        \resumeItem{\textbf{First Place} in the Provincial Olympiad in English of Quang Ngai throughout 2021 - 2022}
      \resumeItemListEnd

    \resumeSubheadTwo
      {Odon Vallet Scholarship}{Aug. 2022}
      \resumeItemListStart
        \resumeItem{Awarded prestigious \textbf{Odon Vallet Fellowship} for academic excellence, issued by Rencontres du Vietnam.}
      \resumeItemListEnd

    \resumeSubheadTwo
        {"Speak Up for Sustainability" English speaking contest}{Apr. 2024}
        \resumeItemListStart
            \resumeItem{\textbf{Encouragement Prize, Top 4} overall in the "Speak Up for Sustainability" English speaking contest, 9th International Students' Day - 2024, hosted by the Executive Committee of the Ho Chi Minh City Student Association and the Vietnam National Union of Students.}
        \resumeItemListEnd



    % \resumeSubheadTwo
    %   {Quang Ngai Provincial Olympiad in English}{Feb. 2022, Nov. 2021}
    %   \resumeItemListStart
    %     \resumeItem{\textbf{First Prize} in both 2022 and 2021 editions, awarded by the Department of Education and Training of Quang Ngai Province.}
    %   \resumeItemListEnd

  \resumeSubHeadingListEnd

\section{Certificates and Events}
    \resumeSubHeadingListStart
    
    \resumeSubhead
      {Workshop on Medical Imaging}{Feb. 2025}
      {Kyoto Institute of Technology and University of Science, VNUHCM}
      \resumeItemListStart
        \resumeItem{Collaborated in a team to use \textbf{3D Slicer} for extracting relevant parts from a human body model, and achieved \textbf{First Place} in the final presentation detailing the technical usage and the impact of parameter tuning on model quality.}
      \resumeItemListEnd

    % \resumeSubhead
    %   {Supervised Machine Learning: Regression and Classification}{Jul. 2024}
    %   {DeepLearning.AI and Stanford University}
    %   \resumeItemListStart
    %     \resumeItem{Completed the online course issued by \textbf{DeepLearning.AI} and \textbf{Stanford University}, covering key concepts in regression and classification.}
    %   \resumeItemListEnd
      
    \resumeSubHeadingListEnd


%----------PROJECTS------------
\section{Selected Projects}
    \resumeSubHeadingListStart        

        % \resumeSubhead{Examined Polyp Segmentation Models}{Jul. 2024 -- Sep. 2024}
        % {AI Research}
        % \resumeItemListStart
        %     \resumeItem{Identified common/unique strengths and weaknesses of two polyp segmentation models (Meta-Polyp vs DuckNet).}
        %     \resumeItem{Analyzed model performance when applied for different image characteristics and model algorithms.}
        % \resumeItemListEnd

        % \resumeSubhead{Analyzed Movie Theater Dataset -- Competition Data Got Talent}{Nov. 2024 -- Dec. 2024}
        % {Data Analysis}
        % \resumeItemListStart
        %     \resumeItem{Extracted insights with Power BI and Jupyter Notebook.}
        %     \resumeItem{Led team workflow and task distribution.}
        %     \resumeItem{Revealed hidden theater location, enabling targeted marketing.}
        %     \resumeItem{Identified hit-movie patterns to inform revenue strategies.}
        % \resumeItemListEnd

        \resumeSubhead{AI-Powered Media Intelligence Platform}{Apr. 2024 -- Jun. 2024} {Backend AI app developer}
        \resumeItemListStart 
        \resumeItem{Developed an AI media platform using \textbf{Django, Elasticsearch, and Celery-Redis} for natural language search and media management.} \resumeItem{Engineered a scalable \textbf{RAG pipeline (LLM, Speech-to-Text, TTS)} to power a \textbf{3D AI assistant} with intelligent query answering and real-time conversational interaction via a controller-worker architecture.}
        \resumeItemListEnd

        \resumeSubhead{Food Schedule App}{Oct. 2024 -- Dec. 2024}
        {Mobile Application Developer}
        \resumeItemListStart
        \resumeItem{Developed a mobile application using Kotlin and Jetpack Compose (UI design), building a backend and database/login system with Django, and fetching food data via Okhttp/Retrofit.}
        \resumeItemListEnd

        \resumeSubhead{\textit{Crossing Road Game}}{Jul. 2024 -- Sep. 2024}
    {C++ / SFML Game Project}
    \resumeItemListStart
        \resumeItem{Developed a 2D arcade game in C++ using SFML, implementing dynamic traffic, collision physics, asset management, and optimizing for a responsive player experience.}
    \resumeItemListEnd

    
    \resumeSubHeadingListEnd
    
%-----------Activities-----------------
\section{Activities}
  \resumeSubHeadingListStart
    
    \resumeSubhead
      {Youth Union Branch Commendation (Youth Union Branch 22APCS2)}{2022--2023}
      {Committee Member -- University of Science, VNU-HCM}
      \resumeItemListStart
        \resumeItem{Received a \textbf{Certificate of Merit} from the Principal for achieving good results in Youth Union organizational work and youth movements during the 2022-2023 academic year.}
      \resumeItemListEnd

    \resumeSubhead
      {Inspire to Aspire Seminar Series}{2023}
      {Organizer -- Ho Chi Minh City, Vietnam}
      \resumeItemListStart
        \resumeItem{Organized a seminar series titled \textit{"Inspire to Aspire"} that connected students with experienced professionals in technology and business, providing career insights and fostering industry awareness.}
      \resumeItemListEnd
      
    \resumeSubhead
      {Asian-Pacific Children's Convention}{Jul. 2015}
      {Youth Delegate -- Fukuoka, Japan}
      \resumeItemListStart
        \resumeItem{Selected by the Ho Chi Minh Communist Youth Union to represent Vietnam at the Asian-Pacific Children’s Convention in Japan, engaging in international cultural exchange activities to promote global understanding, peace, and friendship.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd



%-----------SKILLS------------
\section{Skills}
\vspace{-5mm}
\begin{table}[H]
    \centering
    \begin{tabular}{p{0.25\linewidth}p{0.75\linewidth}}
        Technical Skills: & Scientific Research, Problem Solving, Machine Learning, Computer Vision\\
        Technical Languages: & C/C++, Python, Kotlin, SQL, LaTeX, Markdown, CSS, HTML\\
        Frameworks/Libraries: & Pytorch, Numpy, Pandas, R, Jetpack Compose, SFML\\
        Tools: & Google Colab, Docker, Git/Github, Android SDK, Slicer\\
        Languages: & English (IELTS 8.0), Vietnamese (native)
    \end{tabular}
\end{table}


  
\end{document}